Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
add more explanation in Sec 5.2.2.
better wordings.

%%%%%%%%%%%%%%%%
\subsubsection{Markup for properties}

@@

\noindent Here is an example:

@@

\noindent Note that the {\tt placeholders} library provides better keywords such as {\tt notImplemented} and {\tt todo} and they tells source locations when executed.
Next we write user documentation in Haddock markup:

>>>>

%%%%%%%%%%%%%%%%
\subsubsection{Markup for properties}
\label{sec:markups}

@@

\noindent Here is the example in Section~\ref{sec:markups} again:

@@

\noindent Note that the {\tt placeholders} library provides better keywords such as {\tt notImplemented} and {\tt todo}, which tells source locations when executed.
Next we write user documentation in Haddock markup:
